---
title: "Model"
author: "Huanyu Chen"
output: html_document
---

```{r}
library(readr)
library(dplyr)
library(stringr)
library(corrplot)
library(randomForest)
library(glmnet)
library(sf)
library(spgwr)
library(GWmodel)
library(sp)
```


# Data Preparation

## Census Data Preparation

```{r}
census <- read_csv("./2_output/uhf_summary.csv")
divisor_column <- census[[2]]

census <- census %>%
  mutate_at(vars(3:15), ~ round((. / divisor_column * 100), 3)) %>%
  rename_at(vars(3:15), ~ str_remove(., "^total_"))

write_csv(census, "./3_output/census_precentage.csv")
```

## Merge with three scores

```{r}
scores <- read_csv("./1_output/dat_merge_2_UHF>=15.csv")
dat <- left_join(census, scores, by = "UHF_id") %>%
  arrange(is.na(ParticipantCount)) %>%
  select(-c(total_population, ParticipantCount, mean_td_score, sd_td_score,
         mean_los_score, sd_los_score, mean_ag_score, sd_ag_score))
```

## Weighted Age

```{r}
dat <- dat %>%
  mutate(weighted_age = (12 * ageunder25 +
                         27 * age25to29 +
                         32 * age30to34 +
                         39.5 * age35to44 +
                         49.5 * age45to54 +
                         59.5 * age55to64 +
                         80 * age_above65) / 100,
         weighted_age = round(weighted_age, 3)) %>%
  select(-ageunder25, -age25to29, -age30to34, -age35to44, -age45to54, -age55to64,
         -age_above65)

write_csv(dat, "./3_output/merge_dataset.csv")
```

## Geographic Data

```{r}
geo_data <- st_read("./UHF_42_DOHMH_2009/UHF_42_DOHMH_2009.shp")
# train_dat <- subset(dat[1:nrow(dat), ], !is.na(median_td_score))
```

# Correlation Plot

<!-- ## 7 variables -->

```{r}
dat_selected <- dat %>%
  select(no_health_insurance, bachelor, householdincome, householdnum,
         no_vehicles, weighted_age, employment)

corr_matrix <- cor(dat_selected, use = "complete.obs")
corrplot(corr_matrix, method = "number", type = "full", tl.col = "black")
```

<!-- ## 5 variables: exclude bachelor and household number -->

<!-- ```{r} -->
<!-- dat_selected <- dat %>% -->
<!--   select(no_health_insurance, householdincome, no_vehicles, weighted_age, employment) -->

<!-- corr_matrix <- cor(dat_selected, use = "complete.obs") -->
<!-- corrplot(corr_matrix, method = "number", type = "full", tl.col = "black") -->
<!-- ``` -->

# Linear Regression Model

## Temporal Discounting

```{r}
model_td <- lm(median_td_score ~ no_health_insurance + bachelor + householdincome + 
                 householdnum + no_vehicles + weighted_age + employment, data = dat)
summary(model_td)

par(mfrow = c(2, 2))
plot(model_td)

mean(model_td$residuals^2)
```

## Agency

```{r}
model_ag <- lm(median_ag_score ~ no_health_insurance + bachelor + householdincome + 
                 householdnum + no_vehicles + weighted_age + employment, data = dat)
summary(model_ag)

par(mfrow = c(2, 2))
plot(model_ag)

mean(model_ag$residuals^2)
```

## Loss Aversion

```{r}
# # full model
# model_los_1 <- lm(median_los_score ~ no_health_insurance + bachelor +
#                householdincome + householdnum + no_vehicles +
#                weighted_age + employment, data = dat)
# summary(model_los_1)
# 
# # model excluding bachelor
# model_los_2 <- lm(median_los_score ~ no_health_insurance + 
#                householdincome + householdnum + no_vehicles +
#                weighted_age + employment, data = dat)
# summary(model_los_2)

# model excluding bachelor and household number
model_los_3 <- lm(median_los_score ~ no_health_insurance + householdincome + 
                    no_vehicles + weighted_age + employment, data = dat)
summary(model_los_3)

par(mfrow = c(2, 2))
plot(model_los_3)

mean(model_los_3$residuals^2)
```

## Prediction

```{r}
dat_slr <- dat
dat_subset <- dat[19:nrow(dat), ]

dat_slr[19:nrow(dat), "median_td_score"] <- round(predict(model_td,
                                                          newdata = dat_subset), 2)
dat_slr[19:nrow(dat), "median_ag_score"] <- round(predict(model_ag,
                                                          newdata = dat_subset), 2)
dat_slr[19:nrow(dat), "median_los_score"] <- round(predict(model_los_3,
                                                           newdata = dat_subset), 2)

write_csv(dat_slr, "./3_output/whole_dataset.csv")
```

# GLM: LASSO

```{r}
set.seed(1)
X <- model.matrix(median_td_score ~ no_health_insurance + bachelor + householdincome + 
                 householdnum + no_vehicles + weighted_age + employment,
                 data = dat[1:18, ])[,-1]
y <- dat[1:18, ]$median_td_score

cv.lasso <- cv.glmnet(X, y, alpha = 1, lambda = exp(seq(2, 0, length = 100)))
plot(cv.lasso)
selected_lambda <- cv.lasso$lambda.min
coef(cv.lasso, s = selected_lambda)

# # predict
# newX <- model.matrix(median_td_score ~ no_health_insurance + bachelor + 
#                      householdincome + householdnum + no_vehicles + 
#                      weighted_age + employment, data = dat[19:nrow(dat), ])[,-1]
# 
# dat[19:nrow(dat), "median_los_score"] <- predict(final_model, newx = newX, s = best_lambda)
# 
# write_csv(dat, "./3_output/lasso_dataset.csv")
```

# Random Forest

```{r}
set.seed(1)
model_rf_1 <- randomForest(median_td_score ~ no_health_insurance +
                             householdincome + no_vehicles + weighted_age +
                             employment, data = dat[1:18, ], 
                         importance = TRUE)
print(model_rf_1)

model_rf_2 <- randomForest(median_ag_score ~ no_health_insurance +
                             householdincome + no_vehicles + weighted_age +
                             employment, data = dat[1:18, ], 
                         importance = TRUE)
print(model_rf_2)

model_rf_3 <- randomForest(median_los_score ~ no_health_insurance +
                             householdincome + no_vehicles + weighted_age +
                             employment, data = dat[1:18, ], 
                         importance = TRUE)
print(model_rf_3)
```

Comment: Only `model_rf_3` explains approx. 40% of the variance in the data.

# Geographically Weighted Regression

```{r}
geo_data <- geo_data %>%
  left_join(dat, by = c("UHFCODE" = "UHF_id")) %>%
  slice(-1)

sp_data <- as_Spatial(st_cast(geo_data, "POLYGON"))
sp_data_train <- sp_data[!is.na(sp_data$median_los_score), ]
sp_data_predict <- sp_data[is.na(sp_data$median_los_score), ]
```

## Data Visualization

```{r}
colors <- c("white", "darkred")
spplot(sp_data_train, "median_td_score", col.regions = colorRampPalette(colors)(60),
       cuts = 50, main = "Median Temporal Discounting Score")

colors <- c("white", "darkblue")
spplot(sp_data_train, "median_ag_score", col.regions = colorRampPalette(colors)(60), 
       cuts = 50, main = "Median Agency Score")

colors <- c("white", "darkgreen")
spplot(sp_data_train, "median_los_score", col.regions = colorRampPalette(colors)(60),
       cuts = 50, main = "Median Loss Aversion Score")
```

## Temporal Discounting

```{r}
bwG_td <- gwr.sel(median_td_score ~ no_health_insurance + bachelor + householdincome + 
                    householdnum + no_vehicles + weighted_age + employment, 
                  data = sp_data_train, adapt = FALSE, gweight = gwr.Gauss)

gwrG_td <- gwr(median_td_score ~ no_health_insurance + bachelor + householdincome + 
                 householdnum + no_vehicles + weighted_age + employment,
               data = sp_data_train,
               bandwidth = bwG_td, 
               gweight = gwr.Gauss, 
               hatmatrix = TRUE)
gwrG_td
```

## Agency

```{r}
bwG_ag <- gwr.sel(median_ag_score ~ no_health_insurance + bachelor + householdincome + 
                    householdnum + no_vehicles + weighted_age + employment, 
                  data = sp_data_train, adapt = FALSE, gweight = gwr.Gauss, verbose = FALSE)

gwrG_ag <- gwr(median_ag_score ~ no_health_insurance + bachelor + householdincome + 
                 householdnum + no_vehicles + weighted_age + employment,
               data = sp_data_train,
               bandwidth = bwG_ag, 
               gweight = gwr.Gauss, 
               hatmatrix = TRUE)
gwrG_ag
```

## Loss Aversion

```{r}
bwG_ag <- gwr.sel(median_ag_score ~ no_health_insurance + bachelor + householdincome + 
                    householdnum + no_vehicles + weighted_age + employment, 
                  data = sp_data_train, adapt = FALSE, gweight = gwr.Gauss, verbose = FALSE)

gwrG_los <- gwr(median_los_score ~ no_health_insurance + bachelor + householdincome + 
                householdnum + no_vehicles + weighted_age + employment,
                data = sp_data_train,
                bandwidth = bwG_ag, 
                gweight = gwr.Gauss, 
                hatmatrix = TRUE)
gwrG_los
```

## Performance

```{r}
pairs(as.data.frame(gwrG_td$lhat)[, 2:8])
pairs(as.data.frame(gwrG_ag$lhat)[, 2:8])
pairs(as.data.frame(gwrG_los$lhat)[, 2:8])
```

## Prediction
```{r}
train_coords <- coordinates(sp_data_train)
predict_coords <- coordinates(sp_data_predict)
predictions <- numeric(nrow(sp_data_predict))
local_coefficients <- gwrG_td$SDF@data[, c("X.Intercept.", "no_health_insurance", "bachelor", 
                                           "householdincome", "householdnum", "no_vehicles", 
                                           "weighted_age", "employment")]

for (i in 1:nrow(sp_data_predict)) {
  dists <- spDistsN1(train_coords, predict_coords[i, ], longlat = FALSE)
  nearest_index <- which.min(dists)
  local_coeff <- local_coefficients[nearest_index, ]
  pred_vars <- as.numeric(c(1, sp_data_predict@data[i, c("no_health_insurance", "bachelor", 
                                                         "householdincome", "householdnum", 
                                                         "no_vehicles", "weighted_age", 
                                                         "employment")]))
  predictions[i] <- sum(pred_vars * local_coeff)
}

sp_data_predict$median_td_score_fitted <- predictions
```

```{r}
predictions_ag <- numeric(nrow(sp_data_predict))
local_coefficients <- gwrG_ag$SDF@data[, c("X.Intercept.", "no_health_insurance", "bachelor", 
                                           "householdincome", "householdnum", "no_vehicles", 
                                           "weighted_age", "employment")]

for (i in 1:nrow(sp_data_predict)) {
  dists <- spDistsN1(train_coords, predict_coords[i, ], longlat = FALSE)
  nearest_index <- which.min(dists)
  local_coeff_ag <- local_coefficients[nearest_index, ]
  pred_vars_ag <- as.numeric(c(1, sp_data_predict@data[i, c("no_health_insurance", "bachelor", 
                                                         "householdincome", "householdnum", 
                                                         "no_vehicles", "weighted_age", 
                                                         "employment")]))
  predictions_ag[i] <- sum(pred_vars_ag * local_coeff_ag)
}

sp_data_predict$median_ag_score_fitted <- predictions_ag
```

```{r}
predictions_los <- numeric(nrow(sp_data_predict))
local_coefficients <- gwrG_los$SDF@data[, c("X.Intercept.", "no_health_insurance", "bachelor", 
                                           "householdincome", "householdnum", "no_vehicles", 
                                           "weighted_age", "employment")]

for (i in 1:nrow(sp_data_predict)) {
  dists <- spDistsN1(train_coords, predict_coords[i, ], longlat = FALSE)
  nearest_index <- which.min(dists)
  local_coeff_los <- local_coefficients[nearest_index, ]
  pred_vars_los <- as.numeric(c(1, sp_data_predict@data[i, c("no_health_insurance",
                                                             "bachelor",
                                                             "householdincome",
                                                             "householdnum",
                                                             "no_vehicles",
                                                             "weighted_age",
                                                             "employment")]))
  predictions_los[i] <- sum(pred_vars_los * local_coeff_los)
}

sp_data_predict$median_los_score_fitted <- predictions_los
```

```{r}
sp_data_train$median_td_score_fitted <- gwrG_td$SDF$pred
sp_data_train$median_ag_score_fitted <- gwrG_ag$SDF$pred
sp_data_train$median_los_score_fitted <- gwrG_los$SDF$pred

sp_data <- rbind(sp_data_train, sp_data_predict)

colors <- c("white", "darkred")
spplot(sp_data, "median_td_score_fitted", col.regions = colorRampPalette(colors)(60),
       cuts = 50, main = "Fitted Median Temporal Discounting Score")

sp_data_train$median_ag_score_fitted <- gwrG_ag$SDF$pred

colors <- c("white", "darkblue")
spplot(sp_data, "median_ag_score_fitted", col.regions = colorRampPalette(colors)(60), 
       cuts = 50, main = "Fitted Median Agency Score")

sp_data_train$median_los_score_fitted <- gwrG_los$SDF$pred

colors <- c("white", "darkgreen")
spplot(sp_data, "median_los_score_fitted", col.regions = colorRampPalette(colors)(60),
       cuts = 50, main = "Fitted Median Loss Aversion Score")
```


# Inverse Distance Weighting

# Kriging Interpolation